Statistical Theory\\ Chess Dataset Analysis

### 2024-09-29 Article/Article.tex
Updated Article

>>>>

\section{Methods}
\subsection{Quantile - Quantile Plot}

\subsection{Kolmogorov-Smirnov Test for Normality}
The Kolmogorov-Smirnov (KS) test for normality evaluates whether a sample comes from a normal distribution. It uses the empirical cumulative distribution function (ECDF), $F_n(x)$, of the sample and compares it to the cumulative distribution function (CDF) of the normal distribution, $F(x)$. The test statistic, $D_n$, is defined as:
\[D_n = \sup_x |F_n(x) - F(x)|\]

The null hypothesis $H_0$ assumes that the sample comes from the normal distribution, while the alternative hypothesis $H_1$ posits that it does not.

    If $D_n$ exceeds a critical value (based on the sample size and significance level), we reject $H_0$, concluding the sample deviates significantly from normality.

The KS test is sensitive to both location and shape differences, but less powerful in detecting deviations in the tails of the distribution when compared to other tests like Shapiro-Wilk or Anderson-Darling.

\subsection{Correlation Matrix}
A correlation matrix is a table that displays the pairwise correlation coefficients between multiple variables in a dataset. Each element in the matrix represents the degree of linear relationship between two variables, typically measured by Pearson's correlation coefficient:
\[r_{XY} = \frac{Cov(X,Y)}{\sigma_X\sigma_Y}\]

\subsection{Mann-Whitney U Test}
